### 2022-03-24 Writing/Palaeontology/draft.tex
Updated affiliations

\noindent {\normalsize \sc Thomas Guillerme$^{1,2,*}$, Abigail I. Pastore$^{1}$, and Martin D. Brazeau$^{2,3}$}\\
% Abigail I. Pastore$^{1}$
\noindent {\small \it 
$^1$School of Biological Sciences, University of Queensland, St. Lucia, Queensland, Australia.\\
$^2$Imperial College London, Silwood Park Campus, Department of Life Sciences, Buckhurst Road, Ascot SL5 7PY, United Kingdom.\\
$^3$Department of Earth Sciences, Natural History Museum, Cromwell Road, London, SW75BD, United Kingdom.\\}

% TODO: change the affiliations

>>>>

\noindent {\normalsize \sc Thomas Guillerme$^{1,2,*}$, Abigail I. Pastore$^{2}$, and Martin D. Brazeau$^{3,4}$}\\
% Abigail I. Pastore$^{1}$
\noindent {\small \it 
$^1$School of Biosciences, The University of Sheffield, Sheffield, United Kingdom.\\
$^2$School of Biological Sciences, University of Queensland, St. Lucia, Queensland, Australia.\\
$^3$Imperial College London, Silwood Park Campus, Department of Life Sciences, Buckhurst Road, Ascot SL5 7PY, United Kingdom.\\
$^4$Department of Earth Sciences, Natural History Museum, Cromwell Road, London, SW75BD, United Kingdom.\\}
